Predicting Internet Path Dynamics and Performance with Machine Learning

### 2017-12-20 paper-tex/paper.tex
modify minor error
modifying

\section{Introduction}

1. introduce the original paper: their task, method, and dataset

Internet paths change frequently due to inter/intra-domain routing changes, load balancing, and even misconfigurations and failures. Some of these changes can seriously disrupt performance, causing longer round-trip times, congestion, or even loss of connectivity. Thus, it is of great significant to predict Internet path dynamics and performance.

In the original paper, the authors focus on the problem of predicting Internet path changes and path performance using \texttt{traceroute} measurements. They uses the recent route information of paths (route age for paths, route changes in past, average RTT, etc) to do some predictions of paths. Their are three predict targets: $(i)$ the remaining life time of a route (i.e., the time before a route changes), $(ii)$ the number of route changes in a future timeslot, and $(iii)$ the average RTT  that the path $P$ will experience in the next \texttt{traceroute} measurement.

To achieve these goals, it introduces a NETPerfTrace system, which relies on a standard random forest model for prediction. Moreover it uses extensive evaluation on the impact of different input features by studying the correlations between the inputs and the prediction targets, as well as target selection techniques.

The dataset it provides with is a full week of Paris \texttt{traceroute} measurements performed through the M-Lab open

Internet measurement initiative. The author observes more than 450,000 different paths sampled through Paris-traceroute measurements from more than 180 geo-distributed servers. However, most of the paths are not periodically sampled during this week. And only 2,346 paths have at least 100 \texttt{traceroute} measurements during the analyzed week. So the dataset only contains corresponding infomation of these 2,346 paths.

We find some drawbacks in their data process.

The author processes the data and calculates some statistics for the whole seven days and then use the data to get the ramdon forest model.

\hao{maybe we can put the detail discussion of their data process problems in data analysis part and delete the above sentence only leave the first one.}

And in our own work,firstly we reprocess the provided data in more resonable ways and use the same method (random forest) mentioned by the author to compare the results. Secondly, two other machine learning methods , xgboost and LSTM, are applied to get better performance.

@@

\section{Data Analysis}
\hui{I think this is an important part, who will take this part?}
\heng{Plots of temporally differentiated prediction targets are given here to show their behavior patterns in temporal domain, thus supporting the use of LSTMs.}
With careful review of the data used in the original paper, here we (a) show the authors had used the data incorrectly in the context of making \textbf{predictions} and (b) reveal the temporal properties that the original method failed to employ but perfectly fits LSTMs (long short term memory neural networks), which we later use to improve the performance.

@@

\item 1. \textbf{K\&fix}+RF
\item 2. \textbf{K\&update}+RF
\item 3. \textbf{timeslot\&update}+RF
\item 4. \textbf{origin}+RF
\item 5. \textbf{K\&fix}+xgBoost
\item 6. \textbf{K\&update}+xgBoost
\item 7. \textbf{timeslot\&update}+xgBoost
\item 8. \textbf{origin}+xgBoost
\end{itemize}
\hui{Note}We first predict the route duration instead of resLife. Further study on the difference between these two predicting objective could be conduct if we have time. Currently, we predict the route duration for task 1, because we can only predict this when we use LSTM.

@@

Table 1 describes the $ABC$ in each figure.
\begin{table}[tbp]
	\centering  % 表居中
	\begin{tabular}{lcc} 
		\hline
		Target &$R_r(t)$ &$avgRTT_P(t)$ \\ \hline
		$data-1$ & 0.4016    &0.8124   \\        
		$data-2$ &0.3985 &0.8261 \\        
		$data-3-ws10$  &0.7132 &0.8018 \\
		$data-3-ws20$ &0.6314 &0.7910 \\
		$data-3-ws50$ &0.5359  &0.7790 \\ \hline
	\end{tabular}
	\caption{The $ABC$ of curves
		 in \textbf{Fig.\ref{fig:task1_RF}} and \textbf{Fig.\ref{fig:task3_RF}} }
	 \label{tab:result_RF}
\end{table}
From \textbf{Tab.\ref{tab:result_RF}}, it can be inferred that for target $avgRTT_P(t)$: there is minor difference using five different methods to process the data. They all achieve a relatively good result, which also indicates that for average RTT reported from \texttt{traceroute} measurement, it is not sensitive to the temporal locality. However, for the first predicting target, $R_r(t)$, it is very sensitive to the temporal locality. It changes rapidly as time changes. And to achieve better prediction result, using too much previous data will result in noise and decrease the performance of the model. Because from \textbf{Tab.\ref{tab:result_RF}}, we can clearly observe that $data-3-ws10$ achieves larget $ABC$ compared with other processing methods. It considers only the recent data in a relatively short time slot. Indeed, it is reasonable to get such conclusion, for the remaining life time of a route is always closely related to their route age (which can be indicated from the previous \texttt{traceroute} data).
\subsection{Deep Models}

@@

\begin{document}
	\title{Predicting Internet Path Dynamics and Performance with Machine Leanring}
	%\titlenote{Produces the permission block, and
	%  copyright information}
	%\subtitle{Extended Abstract}
	%\subtitlenote{The full version of the author's guide is available as
	%  \texttt{acmart.pdf} document}

	\maketitle
	\hui{I think we should focus on the process not the final result, which is also important.}
	\section{Introduction}
	1. introduce the original paper: their task, method, and dataset
	Internet paths change frequently due to inter/intra-domain routing changes, load balancing, and even misconfigurations and failures. Some of these changes can seriously disrupt performance, causing longer round-trip times, congestion, or even loss of connectivity. Thus, it is of great significant to predict Internet path dynamics and performance.

	In the original paper, the authors focus on the problem of predicting Internet path changes and path performance using \texttt{traceroute} measurements. They uses the recent route information of paths (route age for paths, route changes in past, average RTT, etc) to do some predictions of paths. Their are three predict targets: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.

	To achieve these goals, it introduces a NETPerfTrace system, which relies on a standard random forest model for prediction. Moreover it uses extensive evaluation on the impact of different input features by studying the correlations between the inputs and the prediction targets, as well as target selection techniques.

	The dataset it provides with is a full week of Paris \texttt{traceroute} measurements performed through the M-Lab open
	Internet measurement initiative. The author observes more than 450,000 different paths sampled through Paris-traceroute measurements from more than 180 geo-distributed servers. However, most of the paths are not periodically sampled during this week. And only 2,346 paths have at least 100 \texttt{traceroute} measurements during the analyzed week. So the dataset only contains corresponding infomation of these 2,346 paths.

	We find some drawbacks in their data process.
	The author processes the data and calculates some statistics for the whole seven days and then use the data to get the ramdon forest model.

	\hao{maybe we can put the detail discussion of their data process problems in data analysis part and delete the above sentence only leave the first one.}

	And in our own work,firstly we reprocess the provided data in more resonable ways and use the same method (random forest) mentioned by the author to compare the results. Secondly, two other machine learning methods , xgboost and LSTM, are applied to get better performance.

	\section{Related Works}
	1. introduce the original paper
	In the original paper, the problem they solve is to use random forest model to predict three labels for one path: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.

	And to achieve these three targets, 69 input features are used to describe the  statistical properties of route dynamics and path latency.
	For the first route dynamic target, the first group of 11 features,referred to as $F_A$, is chosen. It describes the statistical properties (average, minimum, maximum, and percentiles) of the route duration observed for each path.
	And for the second target, the second group of 14 features, as $F_B$, are relevant to the prediction of number of route changes. $F_B$ features take into account the statistical properties of route changes. In addition to that, $F_B$ contains information about the number of route changes observed for a path so far and a binary feature indicating whether a route change occurred for a path in the current time slot. 
	And the last group of 44 features ,referred to as $F_C$ decribes statistical properties of path latency, which is relavent to the prediction of the next \texttt{traceroute} measurement. They calculate the staistical properties of four RTT metrics (average, minimum, maximum and standard deviation) reported from each \texttt{traceroute} measurement.

	\section{Data Analysis}
	\hui{I think this is a important part, who will take this part?}

	\section{Methodol}
	\subsection{Data Processing}

	\section{Experiment}
	\subsection{Classic Models}

	We show the experiment results of the 3 different data we obtained, namely \textbf{K\&fix},\textbf{K\&update},\textbf{timeslot\&update}. We need to find some difference between our 3 data processing methods and the authors', i.e.,\textbf{origin}.

	The experiments we need to conduct are as follows:
	\begin{itemize}

		\item 1. \textbf{K\&fix}+RF
		\item 2. \textbf{K\&update}+RF
		\item 3. \textbf{timeslot\&update}+RF
		\item 4. \textbf{origin}+RF
		\item 5. \textbf{K\&fix}+xgBoost
		\item 6. \textbf{K\&update}+xgBoost
		\item 7. \textbf{timeslot\&update}+xgBoost
		\item 8. \textbf{origin}+xgBoost
	\end{itemize}

	\subsection{Deep Models}

	There are two kinds of input for the LSTM at each timestep, (i) one simple scalar (ii) a vector.
	The experiments we need to conduct are as follows:
	\begin{itemize}
		\item scalar input + LSTM
		\item vector input + LSTM
	\end{itemize}

	\section{Conclusions}
	TODO

\end{document}

>>>>

\section{Introduction}
Internet paths change frequently due to inter/intra-domain routing changes, load balancing, and even misconfigurations and failures\cite{1}.
%  V. Paxson. 1996. End-to-end Routing Behavior in the Internet. In Proceedings of the ACM SIGCOMM 1996 Conference (SIGCOMM ’96). ACM, New York, NY, USA.
Some of these changes can seriously disrupt performance, causing longer round-trip times, congestion, or even loss of connectivity\cite{2}.
%U. Javed, I. Cunha, D. Cho"nes, E. Katz-Bassett, T. Anderson, and A. Krishnamurthy. 2013. PoiRoot: Investigating the Root Cause of Interdomain Path Changes. In Proceedings of the ACM SIGCOMM 2013 Conference on SIGCOMM (SIGCOMM ’13). ACM, New York, NY, USA, 183–194.
Thus, it is of great significant to predict Internet path dynamics and performance.

In the original paper, the authors focus on the problem of predicting Internet path changes and path performance using \texttt{traceroute} measurements. They use the recent route information of paths (route age for paths, route changes in the past, average RTT, etc) to do some predictions of paths. Their are three predict targets: $(i)$ the remaining life time of a route (i.e., the time before a route changes), $(ii)$ the number of route changes in a future timeslot, and $(iii)$ the average RTT  that the path $P$ will experience in the next \texttt{traceroute} measurement.

To achieve these goals, they introduce a $NETPerfTrace$ system, which relies on a standard random forest model for prediction. Moreover, they use extensive evaluation on the impact of different input features by studying the correlations between the inputs and the prediction targets, as well as target selection techniques.

The dataset the authors provide with is a full week of Paris- \texttt{traceroute} measurements performed through the M-Lab open
Internet measurement initiative\footnote{https://www.measurementlab.net/}. They observe more than 450,000 different paths sampled through Paris-\texttt{traceroute} measurements from more than 180 geo-distributed servers. However, most of the paths are not periodically sampled during this week. And only 2,346 paths have at least 100 \texttt{traceroute} measurements during the analyzed week. So the dataset contains corresponding infomation of these 2,346 paths.

We find some drawbacks in their data process.(see section \ref{sec:dataAna} )And in our own work,firstly we reprocess the provided data in more resonable ways and use the same method (random forest) mentioned by the author to compare the results. Secondly, two other machine learning methods , xgboost and LSTM, are applied to get better performance.

@@

\section{Data Analysis}
 \label{sec:dataAna}
\hui{I think this is an important part, who will take this part?}
\heng{Plots of temporally differentiated prediction targets are given here to show their behavior patterns in temporal domain, thus supporting the use of LSTMs.}
With careful review of the data used in the original paper, here we (a) show the authors had used the data incorrectly in the context of making \textbf{predictions} and (b) reveal the temporal properties that the original method failed to employ but perfectly fits LSTMs (long short term memory neural networks), which we later use to improve the performance.

@@

@@

Table 1 describes the $ABC$ in each figure.
\begin{table}[tbp]
	\centering  
	\begin{tabular}{lcc} 
		\hline
		Target &$R_r(t)$ &$avgRTT_P(t)$ \\ \hline
		$data-1$ & 0.4016    &0.8124   \\        
		$data-2$ &0.3985 &0.8261 \\        
		$data-3-ws10$  &0.7132 &0.8018 \\
		$data-3-ws20$ &0.6314 &0.7910 \\
		$data-3-ws50$ &0.5359  &0.7790 \\ \hline
	\end{tabular}
	\caption{The $ABC$ of curves
		 in \textbf{Fig.\ref{fig:task1_RF}} and \textbf{Fig.\ref{fig:task3_RF}} }
	 \label{tab:result_RF}
\end{table}
From \textbf{Tab.\ref{tab:result_RF}}, it can be inferred that for target $avgRTT_P(t)$: there is minor difference using five different methods to process the data. They all achieve a relatively good result, which also indicates that for average RTT reported from \texttt{traceroute} measurement, it is not sensitive to the temporal locality. However, for the first predicting target, $R_r(t)$, it is very sensitive to the temporal locality. It changes rapidly as time changes. And to achieve better prediction result, using too much previous data will result in noise and decrease the performance of the model. Because from \textbf{Tab.\ref{tab:result_RF}}, we can clearly observe that $data-3-ws10$ achieves larget $ABC$ compared with other processing methods. It considers only the recent data in a relatively short time slot. Indeed, it is reasonable to get such conclusion, for the remaining life time of a route is always closely related to their route age (which can be indicated from the previous \texttt{traceroute} data).
\subsection{Deep Models}

@@
